%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Arg 1
    {SDN/NFV Teaching Assistant - \textmd{Department of Computer Science, NYCU}} 
    {Jul. 2023 - Jan. 2024} % Arg 3
    {} % Arg 4
    {
      \begin{cvitems}
        % 只保留 ONOS, L2/L3, Docker, BGP, Segment Routing
        \item {Refined labs for \textbf{ONOS} SDN modules to implement \textbf{L2/L3 protocols}, including Learning Bridge, Proxy ARP, and Unicast DHCP.}
        \item {Led NFV labs on \textbf{Docker}-based routing (\textbf{BGP}) and guided final projects on \textbf{VLAN-based Segment Routing}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \vspace{0.4cm}
%---------------------------------------------------------

  \cventry
    {} % Arg 1
    {Software Engineer Intern - \textmd{IT Department, Makalot Industrial Co., Ltd.}} 
    {Jul. 2022 - Jun. 2023} % Arg 3
    {} % Arg 4
    {
      \begin{cvitems}
        % 拿掉 RBAC, cross-platform, Teams, Outlook 的粗體
        % 只保留 Full-Stack, Vue.js, ASP.NET, OAuth 2.0, JWT, Dapper, Power Automate
        \item {Developed a \textbf{Full-Stack} dashboard using \textbf{Vue.js} and \textbf{ASP.NET Web API} to streamline RBAC and system configurations.}
        \item {Engineered a Dockerized \textbf{OAuth 2.0} Authentication Service with \textbf{JWT} and \textbf{Dapper ORM} to secure cross-platform ERP API access.}
        \item {Implemented RPA workflows via \textbf{Power Automate} to trigger Microsoft Teams and Outlook alerts, reducing manual effort.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \vspace{0.4cm}
%---------------------------------------------------------

  \cventry
    {} % Arg 1
    {Unity Software Engineer (Research Assistant) - \textmd{Department of Multimedia \& Game Development, MUST}} 
    {Jan. 2022 - Jun. 2022} % Arg 3
    {} % Arg 4
    {
      \begin{cvitems}
        % 拿掉 NSTC, cross-platform, real-time, bilingual 的粗體
        % 只保留 Unity, C#, Firebase
        \item {Developed an NSTC project using \textbf{Unity} and \textbf{C\#}, engineering a cross-platform system featuring 5 distinct motion-sensing games.}
        \item {Integrated \textbf{Google Firebase} for real-time data synchronization to support bilingual (English/Chinese) content and learning analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \vspace{0.4cm}
%---------------------------------------------------------

  \cventry
    {} % Arg 1
    {IT Support (Work-Study) - \textmd{Computer and Network Center, NTUT}} 
    {Jun. 2021 - Jun. 2023} % Arg 3
    {} % Arg 4
    {
      \begin{cvitems}
        % 拿掉 technical support (職稱已有), portal 名稱的粗體
        % 只保留 OS installation, Frontend, UI/UX
        \item {Provided technical support to faculty members, handling PC assembly, \textbf{OS installation}, and troubleshooting campus network issues.}
        \item {Participated \textbf{frontend development} of campus Authorized Software Portal, improving \textbf{UI/UX} to streamline software downloads.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}