%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}
\vspace{-0.25cm} % Tighten spacing between title and content

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


  \cventry
    {Master's Thesis / Industry-Academia Collaboration with Wistron NeWeb Corporation (WNC)} % Project Type / Partnership
    {A CI/CD Framework for Zero Downtime Deployment in Wi-Fi Mesh Networks} % Project Title
    {Feb. 2025 - Jan. 2026} % Duration
    {} % Location
    {
      \begin{cvitems}
        \item {Engineered cloud-to-edge CI/CD via \textbf{GitHub Actions} and \textbf{USP (TR-369)}, achieving baseline deployments in \textbf{<30s}.}
        \item {Built a \textbf{C-based controller} via \textbf{UDS} to orchestrate and synchronize \textbf{LXC} updates across a \textbf{3-node prplOS cluster}.}
        \item {Implemented \textbf{iptables} traffic steering for \textbf{Blue-Green/Canary}, eliminating \textbf{50-70ms} downtime with \textbf{0 packet loss}.}
      \end{cvitems}
    }

  \vspace{0.4cm} % Vertical spacing between project entries

%---------------------------------------------------------
  \cventry
    {Industry-Academia Collaboration with Iscom Online International Info. Inc.} % Project Type / Role
    {Multi-Cluster Hybrid Cloud Infrastructure Platform} % Project Title
    {Apr. 2024 - Sep. 2024} % Duration
    {} % Location
    {
      \begin{cvitems}
        \item {Orchestrated a \textbf{3-cluster Kubernetes} hybrid cloud via \textbf{Karmada} and \textbf{GitOps} (ArgoCD/Flux) with weighted scheduling.}
        \item {Implemented \textbf{Cilium Cluster Mesh} and \textbf{HAProxy} for global load balancing, \textbf{cross-cluster failover}, and L7 policies.}
        \item {Engineered multi-cluster observability via \textbf{Thanos} and \textbf{Prometheus} with \textbf{S3-backed} storage and automated alerts.}
      \end{cvitems}
    }

  \vspace{0.4cm} % Vertical spacing between project entries

%---------------------------------------------------------
%---------------------------------------------------------
%---------------------------------------------------------
\cventry
    {Infrastructure Architect (Personal Project)} 
    {Bare-Metal Private Cloud and Container CI/CD Platform}
    {Jan. 2024 - Present} % 日期
    {} 
    {%
      \begin{cvitems} % ★ 這裡直接用 cvitems 就可以了！
        \item {Architected a \textbf{high-availability} cloud hosting \textbf{Nextcloud/Immich} via \textbf{TrueNAS ZFS}, maintaining \textbf{<1\% idle CPU load}.}
        \item {Engineered CI/CD pipelines with a self-hosted \textbf{Harbor} registry for automated \textbf{Dockerized} Next.js deployments.}
        \item {Integrated \textbf{S3-compatible} object storage (\textbf{RustFS}) and \textbf{PostgreSQL} (\textbf{Prisma}) to power a product-grade \textbf{CMS} platform.}
        \item {Secured infrastructure via \textbf{Cloudflare WAF} and \textbf{Nginx Proxy Manager} with automated \textbf{SSL/TLS} and \textbf{DDoS} mitigation.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}